---
title: "Outlier Checking Site A1, A2 and A3"
author: "Nur Rohadatul Aisy"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load, message=FALSE}
library(tidyverse)
library(shiny)
library(imputeTS)
library(ggpubr)
library(zoo)
library(knitr)

Site_A <- read.csv("D:/Outlier_checking/Outlier_checking_site_A.csv")
```

### Overview of Site A datasets 
```{r data}
head(Site_A)
glimpse(Site_A)
```

### Checking the total number of missing values for each columns
```{r Missing-Values}
colSums(is.na(Site_A))
```

## Imputation with `ImputeTS`
A packages with imputation functions, missing data visualizations, stat and datasets.

### The distribution of missing data
```{r Missing-Data-Plots, echo=FALSE, fig.show='hold', out.width='30%'}
ggplot_na_distribution(Site_A$Var.1)
ggplot_na_distribution(Site_A$Var.2)
ggplot_na_distribution(Site_A$Var.3)
```

### Imputation by Linear Interpolation
```{r Spline-Interpolation}
Site_A_imp <- Site_A %>%
  na_interpolation(option="linear")
```

```{r imputation-plot, echo=FALSE, fig.show='hold', out.width='50%' }
ggplot_na_imputations(Site_A$Var.1, Site_A_imp$Var.1)
ggplot_na_imputations(Site_A$Var.2, Site_A_imp$Var.2)
ggplot_na_imputations(Site_A$Var.3, Site_A_imp$Var.3)
```

### Checking Outlier for Site A
```{r Boxplot, echo=FALSE, fig.show='hold', out.width='30%'}
Site_A_imp$Site=as.factor(Site_A_imp$Site)

ggplot(Site_A_imp, aes(x=Site, y=Var.1)) + geom_boxplot()
ggplot(Site_A_imp, aes(x=Site, y=Var.2)) + geom_boxplot()
ggplot(Site_A_imp, aes(x=Site, y=Var.3)) + geom_boxplot()
```

### Filtering Outliers
```{r remove-outliers, fig.show='hold', out.width='30%'}
Site_A_imp <- Site_A_imp %>%
  mutate(is_outlier1 = Var.1 > 1000, 
         is_outlier2 = Var.2 > 10000, 
         is_outlier3 = Var.3 > 1000) %>%
  filter(!is_outlier1, !is_outlier2, !is_outlier3)
```

### Site A Annual Summary
```{r annual-mean, message = FALSE}
Annual_Mean <- Site_A_imp %>% 
  group_by(Site, Year) %>%
  summarize(annual_mean_Var.1 = mean(Var.1), 
            annual_mean_Var.2 = mean(Var.2), 
            annual_mean_Var.3 = mean(Var.3)) %>%
  arrange(Site)
```

### Site A1 Annual Mean
```{r display-site1, echo=FALSE}
Annual_Mean %>%
  filter(Site==1) %>%
  kable()
```

### Site A2 Annual Mean
```{r display-site2, echo=FALSE}
Annual_Mean %>%
  filter(Site==2) %>%
  kable()
```

### Site A3 Annual Mean
```{r display-site3, echo=FALSE}
Annual_Mean %>%
  filter(Site==3) %>%
  kable()
```

## Data Visualization
### Graph of annual mean of Var.1 against time
```{r plot-Var.1, echo=FALSE, fig.align='center'}
ggplot(Annual_Mean, aes(x=Year, y=annual_mean_Var.1, color=Site)) +
  geom_line() + 
  labs(
    title = "Annual Mean Var.1 for Site A",
    x = "Year",
    y = "Var.1")
```

### Graph of annual mean of Var.2 against time
```{r plot-Var.2, echo=FALSE, fig.align='center'}
ggplot(Annual_Mean, aes(x=Year, y=annual_mean_Var.2, color=Site)) + 
  geom_line() +
  labs(
    title = "Annual Mean Var.2 for Site A",
    x = "Year",
    y = "Var.2")
```

### Graph of annual mean of Var.3 against time
```{r plot-Var.3, echo=FALSE, fig.align='center'}
ggplot(Annual_Mean, aes(x=Year, y=annual_mean_Var.3, color=Site)) + 
  geom_line() +
  labs(
    title = "Annual Mean Var.3 for Site A",
    x = "Year",
    y = "Var.3")
```